### 2014-12-09 Draft/abstract.tex
Laurie's comments

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing tools for checking formal temporal constraints.
\textit{The goal of this work is to assist developers construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
To address this issue,
we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and the \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.

>>>>

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing tools for checking formal temporal constraints.
\textit{The goal of this work is to assist developers to construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
To address this issue,
we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and the \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.

### 2014-12-09 Draft/approach.tex
Laurie's comments

\begin{figure}
	\centering
		\includegraphics[scale=0.45]{approach.eps}
	\caption{Overview of \tool\ approach}
	\label{fig:approachOverview}
\end{figure}

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
\tool\ consists of following six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
Additionally, there is an optional model trainer component and external NLP parser component.
We next describe each component in detail.

%The preprocessor accepts API documents and preprocesses the sentences in the method description,
%such as annotating sentence boundaries and reducing lexical tokens.
%The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
%The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
%The semantic graph generator accepts the API documents and generates the semantic graphs that are leveraged by constraint extractor component.
%The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
%Finally, the constraint extractor leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
%We next describe each component in detail.

@@

The preprocessor accepts the API documents and extracts method descriptions.
In particular, the preprocessor extracts the following fields from the method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary and type information of parameters of the API method}, 
3) \textit{Summary and type information of return values of the method}, and
4) \textit{Summary and type information of exceptions thrown (or errors returned) by the methods}.

@@

After extracting desired information, the natural language text is further preprocessed to be analyzed by subsequent components.
The preprocessing steps are required to increase the accuracy of core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
The preprocessor first employs the heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
%From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
%However, this component can be implemented using any other existing NLP libraries or approaches.
In particular, each sentence is annotated with: \textit{1) POS tags, 2) named-entity annotations, and 3) Stanford-typed dependencies.}
For more details on these techniques and their application, please to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

This component accepts the annotated sentence from the previous component,
then using a trained model classifies whether a sentence describes a temporal constraint or not. We next describe the model construction.

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences. 
From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the model, since \tool\ seeks to achieve only a binary classification of the API sentences.
For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
The model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.

Feature selection is an important factor for the accuracy any classification method.
%For instance, na{\"i}ve Bayes classifier assumes each feature independently contributes towards the final probability of classification.
In the simplest form, each word occurring in a sentence is considered as a feature. However, such an approach may lead to overly specific models, and therefore \tool\ approach employs preprocessing for generic features. We next describe the features we chose for training our model along with the rationale for selecting such features.

@@

@@

We use this feature set to train a classier to perform binary classification of temporal constraint sentence vs other sentences. The rationale of using ML based approach as opposed to a rule based approach is because: 1) rule-writing requires domain expertise, 2) rules-writing tends to quickly become ad hoc thus requires greater effort to generate generic rules, and 3) ML classifiers have shown to scale well with large volumes of data.

@@

The text analysis engine component accepts the sentences identified as constraint sentences and creates an intermediate representation of each sentence.
We define our representation as a tree structure that is essentially a FOL expression.
Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.

@@

The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
As shown in figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. A catch all dependency is selected by a parser when no other appropriate dependency can be selected. We thus break down the sentence into two smaller tractable sentences:

@@

Table~\ref{tab:semanticTemplates} lists the semantic templates used in this phase.
Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by \tool\ when the template is applicable.
%All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
Thus our shallow parser breaks the sentence into two individual sentences.

@@

\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentnces, this phase generates an intermediate (FOL) representation of the sentences. This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}. Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}. All the leaf nodes (entities) are represented as the bold words. For readability each node is appended with a number representing the in-order traversal index of the tree.

>>>>

\begin{figure}
	\centering
		\includegraphics[scale=0.45]{approach.eps}
	\caption{Overview of the \tool\ approach}
	\label{fig:approachOverview}
\end{figure}

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of the \tool\ approach.
\tool\ consists of following six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
Additionally, there is an optional model trainer component and external NLP parser component.

First, the preprocessor accepts API documents and preprocesses the sentences in the method description.
%such as annotating sentence boundaries and reducing lexical tokens.
Next, an NLP parser annotates the syntax and semantics of preprocessed sentences.   
The annotated sentences are accepted by candidate identifier component to classify temporal constraint sentences,
using the model trained by the model trainer component.
The text-analysis engine further transforms the identified constraint sentences into the first-order-logic (FOL) representation.
Finally, the constraint extractor leverages the semantic graphs to infer temporal constraints from the FOL representation of a sentence.
The type analyzer component infers temporal constraints encoded in the type system of a language by analyzing the API methods parameter and return types.
We next describe each component in detail.

@@

The preprocessor accepts the API documents and extracts method descriptions.
In particular, the preprocessor extracts the following fields from the method descriptions: 
1) Summary of the API method,
2) Summary and type information of parameters of the API method, 
3) Summary and type information of return values of the method, and
4) Summary and type information of exceptions thrown (or errors returned) by the methods.

@@

After extracting desired information, the natural language text is further preprocessed to be analyzed by subsequent components.
The preprocessing steps are required to increase the accuracy of core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of the \tool\ approach.
The preprocessor first employs the heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12} described in Section~\ref{sub:CoreNLPback}.
%From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
%However, this component can be implemented using any other existing NLP libraries or approaches.
In particular, each sentence is annotated with: \textit{1) POS tags, 2) named-entity annotations, and 3) Stanford-typed dependencies.}

@@

This component accepts the annotated sentence from the previous component,
then using a trained ML model classifies whether a sentence describes a temporal constraint or not. We next describe the model construction.

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API classify the unlabeled sentences as being temporal constraints or not.
From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the ML model, since \tool\ seeks to achieve only a binary classification of the API sentences.
For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
The ML model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.

Feature selection is an important factor for the accuracy any classification method.
%For instance, na{\"i}ve Bayes classifier assumes each feature independently contributes towards the final probability of classification.
In the simplest form, each word occurring in a sentence is considered as a feature. However, such an approach may lead to overly specific ML models, and therefore the \tool\ approach extracts generic features from sentences. We next describe the features we chose for training our ML model along with the rationale for selecting such features.

@@

	\item \textbf{Sentence Structure}: The feature is the ordered sequence of chunking tags~\cite{Klein03,KleinNIPS03} in a sentence. Chunking seeks to divide a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Thus chunking captures the structure of a sentence. Rationale for selecting ordered sequence of chunking tags is to incorporate structure of a sentence as a feature.

@@

We use the described feature set to train a classier to perform binary classification of temporal constraint sentence vs other sentences. The rationale of using ML based approach as opposed to a rule based approach is because: 1) rule-writing requires domain expertise; 2) rules-writing tends to quickly become ad hoc thus requires greater effort to generate generic rules; and 3) ML classifiers have shown to scale well with large volumes of data.

@@

The text analysis engine component accepts the sentences identified as constraint sentences and creates an intermediate representation of each sentence.
This intermediate representation is leveraged by subsequent component to infer formal constraints.
We define our representation as a tree structure that is essentially a FOL expression.
Research literature provides evidence of the adequacy of using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring, pandita13:WHYPER}.

@@

The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
As shown in Figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. A catch all dependency is selected by a parser when no other appropriate dependency can be selected.
The \tool\ approach thus automatically break down the sentence into two smaller tractable sentences:

@@

Table~\ref{tab:semanticTemplates} lists the semantic templates used in this phase.
Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by \tool\ when the template is applicable.
%All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
With respect to the previous example the template 3 \textit{(A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
Thus our shallow parser breaks the sentence into two individual sentences.

@@

\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentences, this phase generates an intermediate (FOL) representation of the sentences. This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}. Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}. All the leaf nodes (entities) are represented as the bold words. For readability each node is appended with a number representing the in-order traversal index of the tree.

### 2014-12-09 Draft/evaluation.tex
Laurie's comments

	\item\CodeIn{java.io} : is one of a popular packages in \CodeIn{Java} programming language. The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by any programming language.
\end{itemize}
We chose \CodeIn{Amazon S3}, \CodeIn{PayPal payment}, and \CodeIn{java.io} APIs as our subjects because they are popular and contain decent documentation.

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the subject APIs.
First two authors manually labeled each sentence in the Java API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently.
We use these classified sentences as the golden set for evaluating effectiveness of \tool.
Table~\ref{tab:results} lists the subject statistics.
Based on the discussions with regards to annotation of \CodeIn{java.io} API, first author annotated the rest of the subject APIs.

@@

We then use these measures to identify relative effectiveness of \tool\ by executing multiple classifiers on the annotated sentences.
We tested the classifiers using a stratified n-fold cross-validation approach,
using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}.
The cross validation ensures that every sentence is used for training and testing,
thus producing low bias and variance.
In particular, we execute the classifiers in two different configurations.
First we executed the classifiers using the words in the sentences as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
We next executed the classifiers on the features proposed by \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$). 
Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are indicative of effectiveness of the constraint statements inferred using the features proposed by \tool\ approach.

To answer RQ2, we manually verified the temporal constraints inferred from constraint sentences by \tool.
However, we excluded the type-enforced temporal constraints inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as eclipse. 
We then measure $accuracy$ of \tool\ as the ratio of the total number of temporal constraints that
are correctly inferred by \tool\ to the total number of constraint sentences. Two authors
independently verified the correctness of the temporal constraints inferred by \tool.
We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints
to the total number of constraint sentences. 
Higher value of \CodeIn{accuracy} is indicative of effectiveness of \tool\ in inferring temporal constraints from constraint sentences.

>>>>

	\item\CodeIn{java.io} : is one of the widely used packages in \CodeIn{Java} programming language. The package provides APIs for system input and output through data streams, serialization and the file system, which are one of the fundamental functionalities provided by any programming language.
\end{itemize}
We chose \CodeIn{Amazon S3}, \CodeIn{PayPal payment}, and \CodeIn{java.io} APIs as our subjects because they are widely used and contain relevant documentation.

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the subject APIs.
The first two authors manually labeled each sentence (2417 total) in the Java API documentation as being a temporal constraint sentence or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently.
We use these classified sentences as the golden set for evaluating effectiveness of \tool.
Table~\ref{tab:results} lists the subject statistics.
Based on the discussions with regards to annotation of \CodeIn{java.io} API, first author annotated the rest of the subject APIs.

@@

We then use these measures to identify relative effectiveness of \tool\ by executing multiple classifiers on the annotated sentences.
We tested the classifiers using a stratified n-fold cross-validation approach,
using 10 as the value n (10-fold) as recommended by Han et al.~\cite{han2006data}.
The cross validation ensures that every sentence is used for training and testing,
thus producing low bias and variance.
In particular, we execute the classifiers in two different configurations.
First we executed the classifiers using the words in the sentences as features and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{wrd}$, R$_{wrd}$, and F$_{wrd}$.
We next executed the classifiers on the features proposed by the \tool\ approach and measure \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{ftr}$, R$_{ftr}$, and F$_{ftr}$.
We next calculate relative gain in \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-Score} as P$_{\Delta}$ (P$_{ftr}$- P$_{wrd}$), R$_{\Delta}$ (R$_{ftr}$ - R$_{wrd}$), and F$_{\Delta}$ (F$_{ftr}$ - F$_{wrd}$). 
Higher values of P$_{\Delta}$, R$_{\Delta}$, and F$_{\Delta}$ are indicative of effectiveness of the constraint statements inferred using the features proposed by the \tool\ approach.

To answer RQ2, we manually verified the temporal constraints inferred from constraint sentences by \tool.
However, we excluded the type-enforced temporal constraints inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as the Eclipse. 
We then measure $accuracy$ of \tool\ as the ratio of the total number of temporal constraints that
are correctly inferred by \tool\ to the total number of constraint sentences. Two authors
independently verified the correctness of the temporal constraints inferred by \tool.
We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints
to the total number of constraint sentences. 
Higher value of \CodeIn{accuracy} is indicative of effectiveness of \tool\ in inferring temporal constraints from constraint sentences.

### 2014-12-09 Draft/introduction.tex
Laurie's comments

\textit{The goal of this work is to assist developers construct API clients that comply with
	temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}

First step towards formalizing temporal constraints is to identify the sentences describing such constraints.
A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
However, the effectiveness of such approach is limited by the quality of the keywords used.
Furthermore, sentences involving temporal constraints oftentimes may not have have uniquely identifiable keywords.

For instance, consider the sentences from \paypalAPI:
1) ``\textit{Use this call to complete a payment.}'' 
2) ``\textit{Use this method to refund a completed payment.}''
Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
In contrast, sentence 2 is a descriptive statement about complete payment method.
Since these sentences are not significantly different in terms of words, a simple keyword-based search will fail to distinguish between the two. 
Another problem with keyword-based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
The large number of keywords further negatively affects accuracy.

Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which may often not be implicit. Consider Sentence 2 in preceding paragraph. The phrase \textit{``completed payment''} refers to the ``Execute Payment'' method in the API.

@@

A ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
This combination allows our approach to make a finer grained distinction between the example sentences described earlier.
To identify the phrases as method-invocation instances, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

In summary, \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
This paper makes the following main contributions:

>>>>

\textit{The goal of this work is to assist developers to construct API clients that comply with temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}

The first step towards formalizing temporal constraints is to identify the sentences describing such constraints.
A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
However, the effectiveness of such approach is limited by the quality of the keywords used.
Furthermore, sentences involving temporal constraints often the time may not have uniquely identifiable keywords.

For instance, consider the sentences from \paypalAPI:
1) ``\textit{Use this call to complete a payment.}'' from \CodeIn{execute payment} method.
2) ``\textit{Use this call to refund a completed payment.}'' from \CodeIn{refund sale} method.
Sentence 1 is a descriptive statement about complete payment method.
In contrast, Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
Since these sentences are not significantly different in terms of words, a simple keyword-based search will fail to distinguish between the two. 
Another problem with keyword-based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
The large number of keywords further negatively affects accuracy.

Even after a sentence has been identified as a constraint sentence, an approach has to infer the references to the method in the sentences, which may often not be implicit. Consider Sentence 2 in preceding paragraph. The phrase \textit{``completed payment''} refers to the \CodeIn{execute payment} method in the API.

@@

A ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
This combination allows \tool\ to make a finer grained distinction between the example sentences described earlier.
Furthermore, to identify the phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.

In summary, the \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
This paper makes the following main contributions:

### 2014-12-09 Draft/related.tex
Laurie's comments

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. In contrast, \tool\ approach works with API documents.
%The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
%In contrast, often the sentences in API documents are not well-formed.
%Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
Pandita et al.~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from their work as follows.
\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach. \tool\ significantly extends the infrastructure used by Pandita et al.~\cite{pandita12:inferring} in following dimensions.
First, \tool\ relies on ML to identify the temporal constraint sentences. The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
Second, \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

>>>>

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. In contrast, the \tool\ approach works with API documents.
%The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
%In contrast, often the sentences in API documents are not well-formed.
%Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
Pandita et al.~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from their work as follows.
\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach. \tool\ significantly extends the infrastructure used by Pandita et al.~\cite{pandita12:inferring} in following dimensions.
First, \tool\ relies on ML to identify the temporal constraint sentences. The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
Second, the \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.
